%-------------------------
% Resume in Latex
% Author : Adeland Luo
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-15pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-20pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}
\newcommand{\resumeItem}[1]{
  \item\small{
    \textbullet\hspace{0.5em}{#1 \vspace{-2pt}}
  }
}


\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-15pt}}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Adeland Luo} \\ \vspace{3pt}
    \small
   \hspace{.5pt}{}
    $|$
    \hspace{.5pt} \href{mailto:}{}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/adelandluo/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/adeland}{GitHub} 
\end{center}
%----------- \\EDUCATION -----------

\section{\hspace{.35cm}Education}
\vspace{10pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
    {\hspace{4mm}University at Buffalo}{ Buffalo, New York}
    {\hspace{4mm}Bachelors of Science in Computer Science\textbf{}}{December 2025 } 


     \vspace{-10pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sameasy Design \& Print}{Brooklyn, New York}
      {Graphic Design Assistant}{Jul 2021 \textbf{--} Aug 2023}
      \vspace{1pt}
        \resumeItemListStart
            \resumeItem{Designed and edited advertisements for over 200 local businesses utilizing Adobe Photoshop. }
            \resumeItem{Created custom merchandise and printed large banners for clients with RIP Queue and Graphtec.}  
        \resumeItemListEnd
    \resumeSubheading
      {MakerState}{New York, New York}
      {STEM Instructor}{Feb 2022 \textbf{--} Aug 2022}
      \vspace{1pt}
        \resumeItemListStart
            \item {Taught 10 cohorts of younger students basics in Scratch and how to create functional code alongside programming basics for objects and robotics in Lego Mindstorms.}
            \item{Instructed 15 classes of 20 students on designing and printing 3-D models in TinkerCAD.}
            \item{Crafted STEM curriculum, featuring TinkerCAD modeling projects, Scratch programming problems, and informative lectures on fundamental programming principles to challenge students.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd




%----------- PROJECTS -----------

\section{Projects}
    \vspace{1pt}
    \resumeSubHeadingListStart
     \resumeProjectHeading
        {\textbf{OmniSense $|$ (MATLAB, Stable Diffusion, Adobe Photoshop)}}{}
            \resumeItemListStart
            \smallskip
            \resumeItem{Challenge winning hackathon project that utilizes MATLAB simulations of software-defined radios emitting monostatic radio frequency waves.}
            \resumeItem{Aimed at assisting visually impaired users by informing them of any possible obstructions or objects approaching them in a 360 degree radius.}
          \resumeItemListEnd
          \resumeProjectHeading
        {\textbf{InnerMosaic $|$ (TensorFlow, React Native, Flask)}}{}
            \resumeItemListStart
            \smallskip
            \resumeItem{Hackathon project integrating AI with traditional journaling methods to give users insightful feedback on their journal entries.}
            \resumeItem{Trained learning module on 1473 journal entries to match words with emotions utilizing BERT.}
            \resumeItem{Model outputs a mood-sphere based on found sentiments to help users visualize their emotional landscape. }
          \resumeItemListEnd
           \resumeProjectHeading
        {\textbf{Local $|$ (TypeScript, Flask, React)}}{}
            \resumeItemListStart
            \smallskip
            \resumeItem{Hackathon project implementing an AI learning module that matches users with $\sim$1000 local companies and startups in the Buffalo-Niagara area.}
            \resumeItem{Features an interactive map of company locations and interview processes to assist users.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Trading Models $|$ (Python, Pandas, Zipline)}}{}
          \resumeItemListStart
          \smallskip
            \resumeItem{In-progress Python project focused on modeling market data and formulating trading strategies for backtesting on historical American financial markets.}
            \resumeItem{Aimed at gaining insights into the impact of volatility and risk factors on decision-making processes during strategy development.}
            \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Visual Novel $|$ (Python, Ren'Py, Stable Diffusion)}}{}
            \resumeItemListStart
            \smallskip
            \resumeItem{In-progress novel game written in Ren’Py driven by user input with 13 varying endings based on user decisions.}
            \resumeItem{Over 500 differing character and background arts generated utilizing NovelAI image diffusion engine version 2.}
          \resumeItemListEnd

    
    \resumeSubHeadingListEnd
%----------- SKILLS ----------- 

\section{Skills}
  \vspace{4pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Frameworks \& Programming Languages}{ Proficient: Python $|$ Familiar: Java, C++, HTML, TensorFlow, React, Flask, MongoDB, Docker, Pandas, Autodesk, Microsoft Office, Adobe Photoshop. } \\ \vspace{3pt}
        
        \textbf{Languages}{ English, Chinese.}
        
    }}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
